Blas\'e3D

### 2023-11-14 paper/paper2/ms.tex
Add intro text to the paper

>>>>

Precomputed synthetic stellar spectral models represent a distillation of all available physics and chemistry theory into effortlessly-reproducible comparisons for spectral observations.  Practitioners may simply download a file and overplot it against an observed spectrum, and apply human pattern recognition to obtain insights on fundamental stellar properties.  But such exercises typically fall short.  Inevitably, individual line depth and shape predictions do not match the observed spectrum.   \citet{2022ApJ...941..200G} introduced a two-stage interpretable Machine Learning (ML) technique to alleviate some of these challenges.  First clone the lines in a precomuted spectrum with fine-tuned Voigt profiles, and then warp those line properties in response to data using the power of automatic differentiation.  This design satisfied a common use case, the desire to obtain a semi-empirical super-resolution stellar template for the observed star: the pristine $R=\frac{\lambda}{\delta \lambda}\sim1,000,000$ emergent spectrum coming from a patch of the star, having accounted for rotational broadening, instrumental resolution, and telluric artifacts.  We called this algorithm \emph{blas\'e}.

This capability alone was useful for Extreme Precision Radial Velocity (EPRV), but a key limitation of \emph{bla\'e} was its requirement to pre-select a grid point as the initial starting point.
